Viscous Transport in Eroding Porous Media

### 2019-10-13 docs/transport/erosion_transport.tex
NM

Flow in porous media is further complicated when boundaries dynamically
evolve in response to the fluid flow. This coupling between the geometry
and the flow occurs, for example, in applications involving
melting~\citep{bec-vis1998, rycroft2016asymmetric, jambon2018singular,
favier2019rayleigh, morrow2019moving},
dissolution~\citep{kan-zha-che-he2002, mac2015shape, moo2017,
wykes2018self}, deposition~\citep{joh-eli1995, hewett2018modelling},
biofilm growth~\citep{tan-val-wer2015}, and crack
formation~\citep{cho2019crack}. We focus on erosion, a fluid-mechanical
process that is prevalent in many geophysical, hydrological, and
industrial applications~\citep{berhanu2012shape, hewett2017evolution,
lachaussee2018competitive, lopez2018cfd, allen2019sde, amin2019role}.
When a porous medium erodes, certain qualitative characteristics are
unveiled that affect transport through the geometry.  For example, an
eroded geometry may contain channels of high porosity, which, though few
in number and modest in volume fraction, transmit a large portion of the
flux~\citep{qua-moo2018}. This arrangement results in velocities that
vary over several orders of magnitude~\citep{all-hea-lab-rei2002}.
Moreover, channelization creates heterogeneous and anisotropic medium
properties, which affect the transport of tracers such as
contaminants~\citep{cve-che-wen1996, dag1987, kon-bre1978} and
heat~\citep{nil-sto1990, ree-sto1995}.

>>>>

\todo[inline]{The above set of references for ``examples of course-grained models" seems very thorough and perhaps not as relevant as other references on erosion, melting, etc. JFMs reference format makes them take up a lot of space. So if there are references here that you wouldn't mind dropping, it might help. I wouldn't drop all of them. I think at least 3-4 are definitely needed.}

Flow in porous media is further complicated when boundaries evolve 
dynamically in response to the fluid flow. This coupling between geometry
and flow occurs, for example, in applications involving
melting~\citep{bec-vis1998, rycroft2016asymmetric, jambon2018singular,
favier2019rayleigh, morrow2019moving},
dissolution~\citep{kan-zha-che-he2002, mac2015shape, moo2017,
wykes2018self}, deposition~\citep{joh-eli1995, hewett2018modelling},
biofilm growth~\citep{tan-val-wer2015}, and crack
formation~\citep{cho2019crack}. We focus on erosion, a fluid-mechanical
process that is prevalent in many geophysical, hydrological, and
industrial applications~\citep{berhanu2012shape, hewett2017evolution,
lachaussee2018competitive, lopez2018cfd, allen2019sde, amin2019role}.

When a porous medium erodes, certain qualitative characteristics are
unveiled that affect transport through the geometry.  For example, an
eroded geometry may contain channels of high porosity, which, though few
in number and modest in volume fraction, transmit a large portion of the
flux~\citep{qua-moo2018}. This arrangement results in velocities that
vary over several orders of magnitude~\citep{all-hea-lab-rei2002}.
Moreover, channelization creates heterogeneous and anisotropic medium
properties, which affect the transport of tracers such as
contaminants~\citep{cve-che-wen1996, dag1987, kon-bre1978} and
heat~\citep{nil-sto1990, ree-sto1995}.
